Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-03 paper/src/paper.tex
paper minor fixes.

\acmConference[SC’17]{Supercomputing}{May 29 -- June 2}{Orlando, FL, USA}

@@

Most common work in the literature consider \textit{a posteriori} optimization
of a scheduling algorithm on a (actual) data set.  The increasing amount and
diversity of data generated by large scale platforms motivate the community to
study more sophisticated policies that could leverage these data.  During the
last few years, there was an explosion of the number of works at the interface
of HPC and BigData fields, dealing with learning algorithms. Recent
sophisticated approaches developed \textit{ad hoc} supervised machine learning
algorithms for reducing uncertainty in problem parameters (e.g.\ job execution
times, memory requirements, etc.). However, only few studies
evaluate the impact of such techniques on the performances of the resource
manager.

@@

  \caption{Variability in the weekly average waiting time in the KTH-SP2 trace
  (see Subsection~\ref{sub:traces}) for 7 different policies. The policy set is
  reduced as not to obstruct the figure.}

@@

  \item The bandit feedback strategy with hyper-parameters $\lambda=1, \Delta
    \in \left\{ 1 \text{day},1 \text{week} \right\}$. The choice of $\lambda=1$
    means that we use no decay in the estimation of the overall cost. Choosing
    to eliminate decay in this experimental campaign is natural since our
    resampled data is in a stationary regime \textit{by construction}, as
    explained in~\ref{ssub:resampling}.

@@

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average total waiting time diminution of fixed policies with respect to EASY(FCFS).}

@@

\begin{equation}
  \frac{\sum_{k=1}^{k=60}\bar{w}(T_k,\text{EASY}(P_i,40h))-
  \bar{w}(T_k,\text{EASY}(\text{FCFS},40h))}{\sum_{k=1}^{k=60}\bar{w}(T_k,\text{EASY}(\text{FCFS},40h))}
\end{equation}

@@

There are two directions to extend this work.  First, the question of
the existence of a more efficient selection strategy for bandit feedback for
these systems is not addressed by this work. Is a simulator really necessary?
%@Denis: a essayer.. 1 mois de travail pour tester?
Second, one can help but wonder what performance could be achieved by extending
the search space to arbitrary policies. This means doing a complete study
including lower bounding the cost and studying learning performance using some
function approximator.
%@Denis: c'est ce que font vasily et salah de deux manieres differentes.
%TODO SPLIT IN TWO, MENTION FACTOR ANALYSIS.
As these directions are data-bound, they will require careful application of
trace resampling techniques in order to be successful.

>>>>

\acmConference[SC’17]{Supercomputing}{November 12 -- 17}{Denver , CO, USA}

@@

Most common work in the literature consider \textit{a posteriori} optimization
of a scheduling algorithm on a (actual) data set.  The increasing amount and
diversity of data generated by large scale platforms motivate the community to
study more sophisticated policies that could leverage these data.  During the
last few years, there was an explosion of the number of works at the interface
of the HPC and Big Data fields, dealing with learning algorithms. Recent
sophisticated approaches developed \textit{ad hoc} supervised machine learning
algorithms for reducing uncertainty in problem parameters (e.g.\ job execution
times, memory requirements, etc.). However, only few studies
evaluate the impact of such techniques on the performances of the resource
manager.

@@

  \caption{Variability in the weekly average waiting time in the KTH-SP2 trace
  (see Subsection~\ref{sub:traces}) for 7 different policies with $\Theta = 0$. The policy set is
  reduced as not to obstruct the figure.}

@@

  \item The bandit feedback strategy with hyper-parameters $\epsilon=0.5,
    \lambda=1, \Delta \in \left\{ 1 \text{day},1 \text{week} \right\}$. The
    choice of $\lambda=1$ means that we use no decay in the estimation of the
    overall cost. Choosing to eliminate decay in this experimental campaign is
    natural since our resampled data is in a stationary regime \textit{by
    construction}, as explained in~\ref{ssub:resampling}.
    The choice of $\epsilon=0.5$ is a reasonable default.

@@

\begin{table*}[]
  \centering
  \ra{1.3}

  \caption{Average total waiting time diminution of fixed policies with respect
  to EASY(FCFS). The precise definition of the value reported is provided in
Eq~\ref{eq:cum}}

@@

\begin{equation}
  \label{ref:cum}
  \frac{\sum_{k=1}^{k=60}\bar{w}(T_k,\text{EASY}(P_i,40h))-
  \bar{w}(T_k,\text{EASY}(\text{FCFS},40h))}{\sum_{k=1}^{k=60}\bar{w}(T_k,\text{EASY}(\text{FCFS},40h))}
\end{equation}

@@

There are two directions to extend this work.  First, the question of
the existence of a more efficient selection strategy for bandit feedback for
these systems is not addressed by this work. Is a simulator really necessary?
%@Denis: a essayer.. 1 mois de travail pour tester?
Second, one can help but wonder what performance could be achieved by extending
the search space to arbitrary policies. This means doing a complete study
including lower bounding the cost and studying learning performance using some
function approximator.
%@Denis: c'est ce que font vasily et salah de deux manieres differentes.
%TODO SPLIT IN TWO, MENTION FACTOR ANALYSIS.
As both these directions are data-bound, they will require careful application of
trace resampling techniques in order to be successful.
